Response to reviewers

### 2022-03-23 reviews/EJOR/01/main.tex
Apply suggestions from proselint
Add minor change
Apply suggestions from Vince's review
Co-authored-by: Vince Knight <vince@vknight.org>

    I would like to thank all the reviewers for their help and comments and for
    the time they took to overhaul the manuscript.
    Their suggestions were very helpful and have been considered to improve the
    manuscript.
    The following changes were made:

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 2: \textit{Since the application in mind
        is the EMS-ED interface, it would be better to write the paper
        immediately from this perspective, instead of first abstracting it
        and then applying it to that problem.}
        \item Reviewer 3 - Comment 8: \textit{Figs 7-11: Row player and
        Column Player are unclear: hospital 1 and hospital 2 would be a
        better choice I presume.}
    \end{itemize}
    The paper is now written more application focused.
    All sections are now presented from the perspective of the EMS-ED
    interface.
    In the game theoretic section instead of row/column player we now use
    hospital A and hospital B.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 4: \textit{To highlight the contributions
        of this work, it is necessary to compare the novelty of this work
        with previous results in the literature.}
    \end{itemize}
    In the new literature review section we now compare the results from
    previous work with the results from this work to highlight the
    contributions of this work.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 6: \textit{Figure 3: about solving the
        Markov chain: the Markov chain is truncated to solve it. Therefore,
        probably N and M are not too small. What about the numerical
        complexity? Because if you just solve it, you have to invert the
        matrix? Is there some structure in the Markov chain that can be
        exploited if N and M would be large?}
        \item Reviewer 3 - Comment 7: \textit{Figures 4-6: why do you
        compare your calculated values with simulation?
        Is it to evaluate the truncations?
        Or are you not sure about the formulas?}
    \end{itemize}
    This is a very good observation.
    As the values of \(N\) and \(M\) increase, the truncated Markov chain
    becomes more complex to solve.
    We have touched upon building a closed-form formula for the steady state
    probabilities but it's still work in progress.
    Figures 4-6 are there to demonstrate the accuracy of our constructed
    model against its discrete event simulation equivalent.
    An additional paragraph is added that talks about truncating the model
    and the old figures have been replaced with ones that compare the
    results from the truncated Markov model with the results from the
    untruncated simulation model.

>>>>

    I would like to thank all the reviewers for their help and comments and for
    the time they took to review the manuscript.
    Their suggestions were extremely helpful and we believe this has resulted in an improved
    manuscript.
    Below is a point by point response and summary of changes made.

@@

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 2: \textit{Since the application in mind
        is the EMS-ED interface, it would be better to write the paper
        immediately from this perspective, instead of first abstracting it
        and then applying it to that problem.}
        \item Reviewer 3 - Comment 8: \textit{Figs 7-11: Row player and
        Column Player are unclear: hospital 1 and hospital 2 would be a
        better choice I presume.}
    \end{itemize}
    The paper is presented with the application of the model as the main focus.
    All sections are now presented from the perspective of the EMS-ED
    interface.
    In the game theoretic section instead of row/column player we now use
    hospital A and hospital B.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 1 - Comment 4: \textit{To highlight the contributions
        of this work, it is necessary to compare the novelty of this work
        with previous results in the literature.}
    \end{itemize}
    In the new literature review section we now directly compare the results from
    previous work with the results from this work to highlight the
    contributions of this work.

    \line(1, 0){0.92\textwidth}
    \begin{itemize}
        \item Reviewer 3 - Comment 6: \textit{Figure 3: about solving the
        Markov chain: the Markov chain is truncated to solve it. Therefore,
        probably N and M are not too small. What about the numerical
        complexity? Because if you just solve it, you have to invert the
        matrix? Is there some structure in the Markov chain that can be
        exploited if N and M would be large?}
        \item Reviewer 3 - Comment 7: \textit{Figures 4-6: why do you
        compare your calculated values with simulation?
        Is it to evaluate the truncations?
        Or are you not sure about the formulas?}
    \end{itemize}
    This observation was really helpful and lead to us conducting more numerical experiments to clarify the point of truncating the state space.
    As the values of \(N\) and \(M\) increase, the truncated Markov chain
    becomes more complex to solve.
    We have touched upon building a closed-form formula for the steady state
    probabilities but that is still a work in progress and not something we are able
    to include in this manuscript.
    Figures 4-6 are there to demonstrate the accuracy of our constructed
    model against its discrete event simulation equivalent and these have been expanded on.
    An additional paragraph is added that talks about truncating the model
    and the old figures have been replaced with ones that compare the
    results from the truncated Markov model with the results from the
    untruncated simulation model. We feel that these extra numeric results 
    do clarify the paper and are thankful for the reviewer comments.
